Side-effects

### 2021-04-14 analysis/side-effects.Rmd

```{r}
event_calls <- cs_count(SE, event, wt=N)
event_site <- cs_count(SE, eval_call_srcref, event) %>% cs_count(event)

left_join(
  select(event_calls, event, n_call=n, p_call=p),
  select(event_site, event, n_site=n, p_site=p),
  by="event"
) %>%
  mutate_if(is.double, ~fmt(., digit=1)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    sanitize.text.function=identity,
    timestamp=FALSE
  )
```

```{r}
filter(SE, event=="rvl") %>% cs_count(class)
```

## Unknwon srcref

```{r}
unknown_srcref <- filter(SE, eval_call_srcref=="???")
```

## Where does the side effects happen

- in the caller - source is `call:fun` where `fun` is the `calle_function` 
  - most of this should be class that do not specify any parameter to `envir`
- in the supplied `envir` parameter -- `in_envir` is true
  - in this case the details are in the `environment_class`
- in a package - the source is `pkg:`
- in the `.userHookEnv` - the source is `userHookEnv`
- in another call
- is S4, R6

```{r}

```

>>>>

```{r}
event <- cs_count(SE, event, wt=N)
event_calls <- cs_count(SE, event)
event_site <- cs_count(SE, eval_call_srcref, event) %>% cs_count(event)

left_join(
  select(event, event, n_event=n, p_event=p),
  select(event_calls, event, n_call=n, p_call=p),
  by="event"
) %>%
  left_join(
    select(event_site, event, n_site=n, p_site=p),
    by="event"
  ) %>% 
  mutate(event=case_when(
    event=="def" ~ "definition",
    event=="asn" ~ "update",
    event=="rvl" ~ "removal"
  )) %>%
  mutate_if(is.double, ~fmt(., suffix="%", digit=1)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    timestamp=FALSE
  )
```

```{r}
event_rvl_class <- filter(SE, event=="rvl") %>% cs_count(class)

overview_table(
  r("event rem from synthetic", percent(filter(event_rvl_class, class=="Synthetic")$p/100)),
  r("event rem from function", percent(filter(event_rvl_class, class=="Function")$p/100)),
  r("event rem from local", percent(filter(event_rvl_class, class=="Local")$p/100))
)
```
